Gazing at the Robot's Head Reflects our Tendency to Anthropomorphise

### 2016-09-06 main.tex
Added computed Mean and SD for section 4.2
But they'll be updated once we use mind attribution questions instead of likeability questions

Running an ANOVA against the change of anthropomorphic attributions
\deltaant before and after the experiment shows that \deltaant is greater for the participants who watched the
human-like tasks ($\Delta_{\text{machine-like}}=TBD (SD=TBD)$
\vs $\Delta_{\text{human-like}}=TBD (SD=TDB)$, $F(1,54) = 6.54, p < .05$\fixme{put the exact
p value here}). In other words, after being exposed to short videos of a robot
performing simple tasks, participants primed with richer cognitive
expectations regarding the robot report a significantly higher tendency to anthropomorphise robots
\emph{in general} (as the questionnaire on anthropomorphic attributions
explicitly referred to \emph{robots in general}).

>>>>

Running an ANOVA against the change of anthropomorphic attributions
\deltaant before and after the experiment shows that \deltaant is greater for the participants who watched the
human-like tasks ($\Delta_{\text{machine-like}}=-0.44 (SD=5.23)$
\vs $\Delta_{\text{human-like}}=3.55 (SD=4.64)$, $F(1,54) = 6.54, p < .05$\fixme{put the exact
p value here}). In other words, after being exposed to short videos of a robot
performing simple tasks, participants primed with richer cognitive
expectations regarding the robot report a significantly higher tendency to anthropomorphise robots
\emph{in general} (as the questionnaire on anthropomorphic attributions
explicitly referred to \emph{robots in general}).
